A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-11 article/02_Materials_and_Methods.Rmd
adjusted figure caption row count

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_construction.jpeg}
\caption{\label{development_burial_construction}Like Figure \ref{development_burial_type}, but for the variable \textit{burial construction}.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_construction.jpeg}
\caption{\label{development_burial_construction}Like Figure \ref{development_burial_type}, but for the variable \textit{burial construction}.\newline\newline}
\end{figure}
